Capstone Movielens Report

### 2025-11-23 reports/capstone-movielens.site/05.appendix.Rmd
Minor fix for function: model.tune.param_range.

::: { #func.model.tune.param_range.details.step8 .sidebar }
  8.Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
```{r eval=FALSE}
    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
    start.idx <- bound.idx["start"]
    end.idx <- bound.idx["end"]

>>>>

::: { #func.model.tune.param_range.details.step8 .sidebar }
  8. Determines endpoints for a new interval of $\lambda$ values in the neighborhood of the minimum *RMSE* value (figured out so far)  with use of the helper function [get_fine_tune.param.endpoints.idx](#func.get_fine_tune.param.endpoints.idx) described above, to improve the accuracy of the *RMSE* calculation in the next iteration:
```{r eval=FALSE}
    bound.idx <- get_fine_tune.param.endpoints.idx(tuned.result)
    start.idx <- bound.idx["start"]
    end.idx <- bound.idx["end"]
